Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-26 manuscript.Rmd
Fine tuning code. All is functional.

--
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
output: pdf_document
---

@@

@@

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
     aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99")

# x1.grob <- ggplotGrob(plotSmallMultiples.1)
# x2.grob <- ggplotGrob(ggplot(cars, aes(speed, dist)) + geom_point())
# 
# library(gtable)
# plot1 <- gtable_filter(x1.grob, 'panel', trim=F)$layout
# pg <- gtable_add_grob(x1.grob, x2.grob, t = max(plot1$t), l = max(plot1$l))
# grid.newpage()
# grid.draw(pg)
```

```{r plotJournalArticle, cache=FALSE}
#=======================================
# Journals
#=======================================
library(gridExtra)

plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count, group=1)) + 
    theme_bw() + 
    geom_line(colour=cp[4], size = 1) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    theme_bw() + 
    geom_line(colour=cp[2], size = 1) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

@@

plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
    theme_bw() + 
    geom_line() +
    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101") + 
    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    #title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    scale_y_continuous(limits = c(.75,2.5)) +
    ylab("Number of Authors") +
    xlab("Year") +
    labs(size = "Standard deviation") +
    labs(colour = "") + 
    scale_colour_manual(values = c("#fdb864", "#e66101")) +
   theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

@@

page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99") + 
    theme_bw() + 
    theme(title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    ylab("Number of Pages") +
    xlab("Year") +
    labs(size = "Standard deviation") +
    labs(colour = "") + 
    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

@@

df1.summarized <- df1 %>% group_by(journal) %>% 
    summarize(EBP.counts = sum(N)) %>% 
    arrange(desc(EBP.counts)) %>%
    slice(1:15)

df1.reduced <- na.omit(df1[df1$journal %in% df1.summarized$journal, ])
df1.reduced <- ungroup(df1.reduced)

df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))

#df1$studyType <- factor(df1$studyType)
j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)]) 
df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)

Text1 <- textGrob("Overall N")
library(gridExtra)

journal.evidence.plot <- ggplot(df1.reduced, 
    aes(x = N, y= journal, group = journal, colour = studyType, shape= studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey90") +
    geom_point(size = 2) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    #facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank(), legend.position = c(.75, .5), 
    legend.title = element_blank(), legend.text = element_text(size = 8)) + 
    xlim(0, 600) + 
    ylab(NULL) +  
    theme(axis.text.x = element_text(hjust = 1, size = 8), axis.ticks = element_blank()) + 
    theme(axis.text.y = element_text(size = 8) ) + 
    scale_x_continuous(breaks = seq(0, 60, 10)) +
    scale_shape_manual(values=c(24, 23, 21, 25))

journal.evidence.plot <- arrangeGrob(journal.evidence.plot, main = textGrob("Overall N", gp=gpar(cex=.7, font=2), vjust = 2, hjust = 1.25))
```

```{r plotPareto}
pareto.df <- df1 %>% group_by(journal) %>% 
    summarize(EBP.counts = sum(N)) %>% 
    arrange(desc(EBP.counts)) %>%
    ungroup() %>%
    mutate(overallCount = sum(EBP.counts, na.rm=TRUE)) %>%
    mutate(percentTotal = (EBP.counts/overallCount) *100) %>%
    mutate(cumSum = cumsum(percentTotal)) %>%
    slice(1:16)

@@

journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
    geom_bar(aes(fill = studyType), stat = "identity") +
    coord_flip() +
    theme_bw() + 
    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 3) +
    labs(x = "Journal", y = "N") +
    ylim(c(0, 150)) +
    scale_fill_manual(values = cp) +
    theme(legend.position = c(.65,.7), panel.grid.major.y = element_blank(), 
          legend.title=element_blank())
```

```{r plotClevelandRelative}

@@

options(digits=3)
proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
    theme_bw() + 
    geom_point() +
    geom_segment(aes(yend = Abbrev, xend = 0)) + 
    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
          legend.position = "none", 
          panel.grid.minor = element_blank(), 
          panel.grid.major.y = element_blank()) + 
    ylab("") + 
    xlab("Proportion") +
    geom_text(aes(x = journalProp + .05, y = Abbrev, label = journalProp), size = 3) +
    xlim(c(0, .5))

@@

```{r}
grid.arrange(journal.evidence.plot, propPlot, 
        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
```

@@

```{r}
#plot.article.count
```

```{r}
plot.author.count
```

```{r}
page.plot
```

@@

```{r}
stacked.plot
```
\newpage
```{r}
journal.evidence.plot
```

\newpage
```{r}
EBP.plot
```

>>>>

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
date: "May 26, 2015"
output: pdf_document
---

@@

```
```{r}

#=======================================
# Journals
#=======================================
library(gridExtra)

plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count, group=1)) + 
    theme_bw() + 
    geom_line(colour=cp[4], size = 1, alpha = .80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Unique Journal Titles") + 
    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    theme_bw() + 
    geom_line(colour=cp[2], size = 1, alpha=.80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Articles Published") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

@@

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
     aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99")
```

@@

plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
    theme_bw() + 
    geom_line() +
    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101", alpha=.60) + 
    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    #title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    scale_y_continuous(limits = c(.75,2.5)) +
    ylab("Number of Authors") +
    xlab("") +
    labs(size = "SD") +
    labs(colour = NULL) + 
    scale_colour_manual(values = c("#fdb864", "#e66101")) +
    theme(axis.title.x = element_text(vjust=-0.5), 
          axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") + 
       theme(title = element_text(size = 10))

@@

page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99", alpha = .60) + 
    theme_bw() + 
    theme(title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    ylab("Number of Pages") +
    xlab("") +
    labs(size = "SD") +
     labs(colour = NULL) +   
    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom")

@@

```{r plotEBPstackedBar}
pareto.df <- df1 %>% group_by(journal) %>% 
    summarize(EBP.counts = sum(N)) %>% 
    arrange(desc(EBP.counts)) %>%
    ungroup() %>%
    mutate(overallCount = sum(EBP.counts, na.rm=TRUE)) %>%
    mutate(percentTotal = (EBP.counts/overallCount) *100) %>%
    mutate(cumSum = cumsum(percentTotal)) %>%
    slice(1:16)

@@

journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
    geom_bar(aes(fill = studyType), stat = "identity", alpha=.60) +
    coord_flip() +
    theme_bw() + 
    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 3) +
    labs(x = "Journal", y = "N") +
    ylim(c(0, 150)) +
    scale_fill_manual(values = cp) +
    theme(legend.position = c(.65,.7),  legend.title=element_blank(), legend.background = element_rect(fill="transparent"))
```

```{r plotEBPproportion}

@@

options(digits=3)
proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
    theme_bw() + 
    geom_point(colour="grey40") +
    geom_segment(aes(yend = Abbrev, xend = 0), colour = "grey40") + 
    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
          legend.position = "none", 
          panel.grid.minor = element_blank(), 
            panel.margin = unit(0,"null")) + 
    ylab(NULL) +
    xlab("Proportion") +
    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 3) +
    xlim(c(0, .5))

@@

@@

```{r}

grid.arrange(plot.author.count, page.plot, ncol = 2)
```

@@

```{r}
stacked.plot
```

\newpage
```{r}
grid.arrange(journal.evidence.plot, propPlot, 
        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
```
